Proposed Solution

### 2017-01-24 CAV17/secs/abs.tex
cav17: motivating example section done

System failures resulting from configuration errors 
are major reasons for compromised reliability of today's software
systems. Although a lot of program verification techniques 
have been proposed, verifying configuration files is still 
an open problem,
because 1) software configurations are typically written in
poorly structured and untyped ``languages'', and 
2) specifying rules for configuration 
verification is challenging in practice.

>>>>

System failures resulting from configuration errors 
are major reasons for compromised reliability of today's software
systems. Although a lot of program verification techniques 
have been proposed, verifying configuration files is, nevertheless, 
an open problem,
because 1) software configurations are typically written in
poorly structured and untyped ``languages'', and 
2) specifying rules for configuration 
verification is challenging in practice.

### 2017-01-24 CAV17/secs/motiv.tex
cav17: motivating example section done

The above example is a complex integer correlation, which implicitly
includes a computational correlation among different entries
in the configuration file.
We call these {\em fine-grained integer correlations}. 
Our tool can detect simple integer correlation---one entry's
value should have a certain correlation with another entry's 
value---as well.
For example, in MySQL, the value of \code{key\_buffer} 
should be larger than \code{max\_allowed\_packet}.
Few existing tools~\cite{yin11anempirical, zhang14encore}
can detect simple integer correlation errors,
but to the best of our knowledge, \app is the first capable of
detecting fine-grained integer correlation errors.

>>>>

This example is a tricky configuration error, which implicitly
includes a computational correlation among different entries
in the configuration file.
We call these errors as {\em fine-grained integer correlations}. 
\app can also detect simple integer correlation: one entry's
value should have a certain correlation with another entry's 
value.
For instance, in MySQL, the value of \code{key\_buffer} 
should be larger than \code{max\_allowed\_packet}.
While several existing tools~\cite{yin11anempirical, zhang14encore}
can detect simple integer correlation errors,
\app is, to the best of our knowledge, the first effort capable of
detecting fine-grained integer correlation errors.
